---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
library("plumberizer")
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# `{plumberizer}`

## Installation

Install the development version from [GitHub](https://github.com/jcrodriguez1989/plumberizer) with:

```{r eval = FALSE}
# install.packages("remotes")
remotes::install_github("jcrodriguez1989/plumberizer")
```

## Useful examples:

We'll show with the [`{emoji}` R package](https://cran.r-project.org/web/packages/emoji/index.html), so install it first `install.packages("emoji")`.

Generate the plumber file for any installed package:

```{r eval = FALSE}
file.edit(plumberizer::plumberize("emoji", "/tmp/emoji_plumber.R"))
```

Run a REST API for any installed package:

```{r eval = FALSE}
plumber::plumb(plumberizer::plumberize("emoji", "/tmp/emoji_plumber.R"))$run()
```

## Usage

`{plumberizer}`'s main function is `plumberize`, call it with the package that you need to generate
a Plumber API configuration file, and it will build it for you:

```{r, eval=FALSE}
plumberizer::plumberize("emoji")
```

```{r, echo=FALSE, results='asis'}
cat(paste0("```\n", plumberizer::plumberize("emoji"), "\n```"))
```
